---
title: "Text As Data R Code"
author: "Howell Lu"
date: "4/28/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Part 1: How to scrape from twitter to create dataset:

```{r}
library(readr)
MTF <- read_csv("C:/Users/howel/OneDrive/Desktop/MTFDFN.csv")
Women <- read_csv("C:/Users/howel/OneDrive/Desktop/WomenArray.csv")
FTM <- read_csv("C:/Users/howel/OneDrive/Desktop/FTMDFN.csv")
Men <- read_csv("C:/Users/howel/OneDrive/Desktop/menArray.csv")

```


Post-Processing  


```{r}
FTMReal<-FTM[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|women|men|woman|ennnnnnnnnnnnbbbbbby|man|gender|ftm|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|lesbian", FTM$Subreddit, ignore.case = TRUE),]
FTMReal<-FTMReal[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|woman|man|women|men|gender|ftm|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|.com", FTMReal$Comments, ignore.case = TRUE),]
MTFReal<-MTF[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|women|men|woman|ennnnnnnnnnnnbbbbbby|man|gender|mtf|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|lesbian", MTF$Subreddit, ignore.case = TRUE),]
MTFReal<-MTFReal[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|woman|man|women|men|gender|mtf|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|.com", MTFReal$Comments, ignore.case = TRUE),]

MenReal<-Men[!grepl("male|men|man|gender|boy|askmen", Men$Subreddit, ignore.case = TRUE),]
MenReal<-MenReal[!grepl("male|men|man|gender|boy|askmen|.com", MenReal$Comments, ignore.case = TRUE),]
WomenReal<-Women[!grepl("female|women|woman|gender|girl|TwoXChromosomes", Women$Subreddit, ignore.case = TRUE),]
WomenReal<-WomenReal[!grepl("female|women|woman|gender|girl|TwoXChromosomes|.com", WomenReal$Comments, ignore.case = TRUE),]

MenReal<-MenReal[!grepl("automoderator", MenReal$User, ignore.case = TRUE),]
WomenReal<-WomenReal[!grepl("automoderator", WomenReal$User, ignore.case = TRUE),]
FTMReal<-FTMReal[!grepl("automoderator", FTMReal$User, ignore.case = TRUE),]
MTFReal<-MTFReal[!grepl("automoderator", MTFReal$User, ignore.case = TRUE),]

```








```{r}

WomenRealS <- sample(nrow(WomenReal),40000)
MenRealS <- sample(nrow(MenReal),40000)
WomenReal <- WomenReal[WomenRealS, ]
MenReal <- MenReal[MenRealS, ]

```




Building a corpus with wordscore:
The first step is to merge

```{r}
library(quanteda)
library(quanteda.corpora)
library(readtext)
library(dplyr)
library(quanteda.textmodels)
library(readr)
library(assertr)
library(caret)
```

```{r}
MenDF <- MenReal$Comments
MenDF<-data.frame(MenDF)
MenCorpus<-toString(MenReal$Comments)
WomenCorpus<-toString(WomenReal$Comments)
```


```{r}
ClassMen<-cbind(MenCorpus, "CisMale")
ClassWomen<-cbind(WomenCorpus, "CisFemale")
CisGender<-rbind(ClassMen,ClassWomen)
CisGenderDF <- tibble(text = CisGender[,1],class = CisGender[,2])
CisGenderDFM <- dfm(CisGenderDF$text,removeNumbers = TRUE, remove_punct = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE)
```

```{r}
ws_base <- textmodel_wordscores(CisGenderDFM, 
                                y = (2 * as.numeric(CisGenderDF$class == "CisMale")) - 1,smooth=1)
```

#Therefore -1 will be Female and 1 will be Male

```{r}
MaleFeat <- sort(ws_base$wordscores, decreasing = TRUE)
MaleFeat[1:100] 
```

```{r}
FemaleFeat <- sort(ws_base$wordscores, decreasing = FALSE)
FemaleFeat[1:100] 
```


```{r}
FTMRealS <- sample(nrow(FTMReal))
MTFRealS <- sample(nrow(MTFReal))

```

```{r}
store<- vector()

for(var in 0:234){
store<-c(store,toString(FTMReal[FTMRealS[(var*100):((var+1)*100)], ]$Comments))  
}

for(var in 0:234){
store<-c(store,toString(MTFReal[MTFRealS[(var*100):((var+1)*100)], ]$Comments))  
}

```

```{r}
labelingwordscore<-vector()

for(var in 0:234){
labelingwordscore<-c(labelingwordscore,paste(("FTM"),var))
}

for(var in 0:234){
labelingwordscore<-c(labelingwordscore,paste(("MTF"),var))
}
```

```{r}
TransCorpus<-corpus(store,docvars = labelingwordscore ,docnames = labelingwordscore)
```

```{r}
TransGenderDFM <- dfm(TransCorpus,removeNumbers = TRUE, remove_punct = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE)
```



```{r}
x<-predict(ws_base, newdata = TransGenderDFM,
        rescaling = "lbg", level = 0.95) 
```

```{r}
buzz<-as.table(x)
```

```{r}
sum(buzz[0:235] < 0)
```
```{r}
sum(buzz[236:470] > 0)
```

The calculation will be done manually as we know that there are exactly 470 subsections of the corpus used. 235 of these subsections are supposed to be male and 235 of these are supposed to be female. 

TP: 229
FP: 13
FN: 6
TN: 222

Accurary: 451/470
F1: 










```{r}
store<- vector()

for(var in 0:149){
store<-c(store,toString(FTMReal[FTMRealS[(var*200):((var+1)*200)], ]$Comments))  
}

for(var in 0:149){
store<-c(store,toString(MTFReal[MTFRealS[(var*200):((var+1)*200)], ]$Comments))  
}

```

```{r}
labelingwordscore<-vector()

for(var in 0:149){
labelingwordscore<-c(labelingwordscore,paste(("FTM"),var))
}

for(var in 0:149){
labelingwordscore<-c(labelingwordscore,paste(("MTF"),var))
}
```

```{r}
TransCorpus<-corpus(store,docvars = labelingwordscore ,docnames = labelingwordscore)
```

```{r}
TransGenderDFM <- dfm(TransCorpus,removeNumbers = TRUE, remove_punct = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE)
```



```{r}
x<-predict(ws_base, newdata = TransGenderDFM,
        rescaling = "lbg", level = 0.95) 
```

```{r}
buzz<-as.table(x)
```

```{r}
sum(buzz[0:150] < 0)
```
```{r}
sum(buzz[151:300] > 0)
```


```{r}
store<- vector()

for(var in 0:0){
store<-c(store,toString(FTMReal[FTMRealS[(var*200):((var+1)*20000)], ]$Comments))  
}

for(var in 0:0){
store<-c(store,toString(MTFReal[MTFRealS[(var*200):((var+1)*20000)], ]$Comments))  
}

```

```{r}
labelingwordscore<-vector()

for(var in 0:0){
labelingwordscore<-c(labelingwordscore,paste(("FTM"),var))
}

for(var in 0:0){
labelingwordscore<-c(labelingwordscore,paste(("MTF"),var))
}
```

```{r}
TransCorpus<-corpus(store,docvars = labelingwordscore ,docnames = labelingwordscore)
```

```{r}
TransGenderDFM <- dfm(TransCorpus,removeNumbers = TRUE, remove_punct = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE)
```



```{r}
x<-predict(ws_base, newdata = TransGenderDFM,
        rescaling = "lbg", level = 0.95) 
```

```{r}
buzz<-as.table(x)
buzz
```























Build a corpus with that


```{r}
library(readr)
MTF <- read_csv("C:/Users/howel/OneDrive/Desktop/MTFDFN.csv")
Women <- read_csv("C:/Users/howel/OneDrive/Desktop/WomenArray.csv")
FTM <- read_csv("C:/Users/howel/OneDrive/Desktop/FTMDFN.csv")
Men <- read_csv("C:/Users/howel/OneDrive/Desktop/menArray.csv")

FTMReal<-FTM[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|women|men|woman|ennnnnnnnnnnnbbbbbby|man|gender|ftm|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|lesbian", FTM$Subreddit, ignore.case = TRUE),]
FTMReal<-FTMReal[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|woman|man|women|men|gender|ftm|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|.com", FTMReal$Comments, ignore.case = TRUE),]
MTFReal<-MTF[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|women|men|woman|ennnnnnnnnnnnbbbbbby|man|gender|mtf|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|lesbian", MTF$Subreddit, ignore.case = TRUE),]
MTFReal<-MTFReal[!grepl("nonbinary|trans|egg|gay|non-binary|female|male|cis|woman|man|women|men|gender|mtf|queer|traaaaaaannnnnnnnnns|boys|girls|lgbt|enby|.com", MTFReal$Comments, ignore.case = TRUE),]

MenReal<-Men[!grepl("male|men|man|gender|boy|askmen", Men$Subreddit, ignore.case = TRUE),]
MenReal<-MenReal[!grepl("male|men|man|gender|boy|askmen|.com", MenReal$Comments, ignore.case = TRUE),]
WomenReal<-Women[!grepl("female|women|woman|gender|girl|TwoXChromosomes", Women$Subreddit, ignore.case = TRUE),]
WomenReal<-WomenReal[!grepl("female|women|woman|gender|girl|TwoXChromosomes|.com", WomenReal$Comments, ignore.case = TRUE),]

MenReal<-MenReal[!grepl("automoderator", MenReal$User, ignore.case = TRUE),]
WomenReal<-WomenReal[!grepl("automoderator", WomenReal$User, ignore.case = TRUE),]
FTMReal<-FTMReal[!grepl("automoderator", FTMReal$User, ignore.case = TRUE),]
MTFReal<-MTFReal[!grepl("automoderator", MTFReal$User, ignore.case = TRUE),]

Menlong<-MenReal[as.numeric(ave(MenReal$User, MenReal$User, FUN=length)) >= 100, ]
Womenlong<-WomenReal[as.numeric(ave(WomenReal$User, WomenReal$User, FUN=length)) >= 100, ]
Ftmlong<-FTMReal[as.numeric(ave(FTMReal$User, FTMReal$User, FUN=length)) >= 100, ]
Mtflong<-MTFReal[as.numeric(ave(MTFReal$User, MTFReal$User, FUN=length)) >= 100, ]

Menlong<-aggregate(Comments ~ User, data = Menlong, c)
Womenlong<-aggregate(Comments ~ User, data = Womenlong, c)
Ftmlong<-aggregate(Comments ~ User, data = Ftmlong, c)
Mtflong<-aggregate(Comments ~ User, data = Mtflong, c)

```



```{r}
MenComments<-cbind(Menlong$Comments,"Male")
WomenComments<-cbind(Womenlong$Comments,"Female")
FTMComments<-cbind(Ftmlong$Comments,"FTM")
MTFComments<-cbind(Mtflong$Comments,"MTF")

```





```{r}
TotalCorpus<-rbind(MenComments,WomenComments,FTMComments,MTFComments)

TotalCorpus <- tibble(text = TotalCorpus[,1],class = TotalCorpus[,2])

TotalCorpusCha<- "1"

```

```{r}

for(var in 1:585){
TotalCorpusCha<-cbind(TotalCorpusCha,toString(unlist(TotalCorpus$text[var])))
}

text<-TotalCorpusCha[2:586]

class = unlist(TotalCorpus$class)

dfmfinal<-data.frame(text,class)
```





```{r}
TotalCorpusDFM <- dfm(dfmfinal$text, remove_punct = TRUE,removeNumbers = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE) %>% 
  dfm_trim(min_termfreq = 12) %>% 
  convert("matrix")
```




```{r}
ids_train <- createDataPartition(1:nrow(TotalCorpusDFM), p = 0.8, list = FALSE, times = 1)
train_x <- TotalCorpusDFM[ids_train, ] %>% as.data.frame()
train_y <- dfmfinal$class[ids_train] %>% as.factor()
test_x <- TotalCorpusDFM[-ids_train, ]  %>% as.data.frame() # test set data
test_y <- dfmfinal$class[-ids_train] %>% as.factor() # test set labels
```

```{r}
baseline_acc <- max(prop.table(table(test_y)))
trctrl <- trainControl(method = "none") 

```


```{r}
mtry <- 3*(sqrt(ncol(train_x)))
ncol(train_x)
mtry
ntree <- 1400
```
```{r}
library(randomForest)

```


```{r}
suppressWarnings(rf.base <- randomForest(x = train_x, y = train_y, ntree = ntree, mtry = mtry, importance = TRUE))
token_importance <- round(importance(rf.base, 2), 2)
head(rownames(token_importance)[order(-token_importance)])
```



```{r}
suppressWarnings(predict_test <- predict(rf.base, newdata = test_x))
```


```{r}
confusionMatrix(data = predict_test, reference = test_y)

```








```{r}
trainControl <- trainControl(method = "cv", number = 5)
metric <- "Accuracy"
mtry <- 3*(sqrt(ncol(train_x)))
ntree <- 1400
tunegrid <- expand.grid(.mtry = mtry)
suppressWarnings(system.time(rf.caret <- train(x = train_x, y = train_y, 
                              method = "rf", metric = metric, 
                              tuneGrid = tunegrid, trControl = trainControl,
                              ntree = ntree)
            ))

# print results
print(rf.caret)

rf.caret$finalModel

suppressWarnings(rf_predict <- predict(rf.caret, newdata = test_x))
confusionMatrix(rf_predict, reference = test_y)

# plot importance
varImpPlot(rf.caret$finalModel, n.var = 10, main = "Variable Importance")
```

















































```{r}
MenCorpus<-toString(MTFReal$Comments)
WomenCorpus<-toString(FTMReal$Comments)
```


```{r}
ClassMen<-cbind(MenCorpus, "CisMale")
ClassWomen<-cbind(WomenCorpus, "CisFemale")
CisGender<-rbind(ClassMen,ClassWomen)

```


```{r}
CisGenderDF <- tibble(text = CisGender[,1],class = CisGender[,2])
```



```{r}
CisGenderDFM <- dfm(CisGenderDF$text, remove_punct = TRUE,removeNumbers = TRUE, remove = c(stopwords("english"),stopwords("german"),stopwords("french"),stopwords("spanish"),stopwords("hungarian"),stopwords("chinese"),stopwords("russian")), tolower = TRUE )
```

```{r}
ws_base <- textmodel_wordscores(CisGenderDFM, 
                                y = (2 * as.numeric(CisGenderDF$class == "CisMale")) - 1,smooth=1)
``` 

#This is a list of the most common male-to-female words.


```{r}
MaleFeat <- sort(ws_base$wordscores, decreasing = TRUE)
MaleFeat[1:100] 
```


#This is a list of the most popular male to female words

```{r}
FemaleFeat <- sort(ws_base$wordscores, decreasing = FALSE)
FemaleFeat[1:100] 
```


































```


